---
title: "Text: Words 2"
author: "zixu liu"
editor: visual
format:
  html:
    embed-resources: true
    code-fold: true  # new
execute:
  echo: true
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(wordcloud)
library(tm)
library(tidytext)
```

# Romeo and Juliet

"Oh Romeo, Romeo, wherefore art thou Romeo?"

Full script - <http://shakespeare.mit.edu/romeo_juliet/full.html>

Let's explore...

1.  Whose name appears more often, Romeo or Juliet?
2.  Perform "pre-cleaning" on the file to remove extraneous characters.
3.  Identify which word appears most often in the text

# Read in Romeo and Juliet

### Option 1 - from file

```{r}
RandJ0 <- read_file("Romeo and Juliet Entire Play.txt")
```

### Option 2 - directly

```         
```

# Term Frequency

Whose name appears more often, Romeo or Juliet?

```{r}
RandJ0_lower <- str_to_lower(RandJ0)
romeo_count <- str_count(RandJ0_lower,"romeo")
juliet_count <- str_count(RandJ0_lower,"juliet")
print(paste("romeo #:", romeo_count))
print(paste("juliet #:", juliet_count))
```

# Pre-cleaning / Tokenize

Perform "pre-cleaning" on the file to remove extraneous characters.

```{r}
stop_word <- readRDS("stopwords_ws.rds")
stop_word <- data.frame(word = stop_word)

```

clean the stop word, sign, punctuation... so that we can focus on some word with meaning

```{r}
RandJ0_cleaned <- RandJ0_lower |>
  str_replace_all("[[:punct:]]", " ") |>
  str_replace_all("\\n", " ") |>
  str_split("\\s+") |>
  unlist()
RandJ0_cleaned_df <- data.frame(word = RandJ0_cleaned)
RandJ0_cleaned_df <-RandJ0_cleaned_df |> 
  anti_join(stop_word)

```

# Wordcloud

In case we get here during in-class coding and you want to access what I have, here are two rds files...that I'll talk about when we get here.

```{r}
RandJ <- readRDS("RandJ.rds")

```

# n-grams

```{r}
#cleaning
RandJ0_cleaned <- RandJ0_lower |>
  str_replace_all("[[:punct:]]", " ") |>
  str_replace_all("\\n", " ") 

bigram_df <- tibble(text = RandJ0_cleaned)

bigram_df <- bigram_df |>
  unnest_tokens(bigram, text, token = "ngrams", n = 2) |>
  separate(bigram, c("word1", "word2"), sep = " ") |> 
  filter(!word1 %in% stopwords("en")) |> 
  filter(!word2 %in% stopwords("en"))
```

# Visualization of n-grams

```{r}
bigram_count <- bigram_df |>
  unite(bigram, word1, word2, sep = " ") |>
  count(bigram, sort = TRUE)
#bigram count table
bigram_count
#visualization
bigram_count |> 
  pull(bigram) |> 
  wordcloud(
    min.freq = 5,
    max.words = 10,
    random.order = FALSE,
  )

```

top 3 bigram:

friar laurence

lady capulet

thou art

Romeo is the most conmon word

Comments:

Reviewer Comments\
\
1. I like that the intro is clear and easy to follow. Maybe just add a quick sentence at the end summarizing what you found overall.\
\
2. The term frequency section makes sense, but it could help to briefly explain what the counts actually tell us about the text.\
\
3. The steps for cleaning and tokenizing are laid out nicely. You could also add one short sentence explaining why those steps are important.\
\
Code Suggestions: Maybe add a few small comments in the code to explain what each step is doing, especially in the preprocessing section.
